Recovery of a deleted deep sequencing data set sheds new light on the early spread of SARS-CoV-2 in Wuhan

### 2021-06-06 paper/paper.tex
narrow region of interest

\subsection{The data are sufficient to determine the viral sequence from the start of spike through the end of ORF10 for many samples}
The approach described by \citet{wang2020medRxiv} involved sequencing PCR amplicons covering nucleotide sites 21,563 to 29,674 of the SARS-CoV-2 genome, which spans from the start of the spike gene to the end of ORF10.
The approach also involved sequencing a short amplicon generated by nested PCR that covered a fragment of ORF1ab spanning sites $\sim$15,080 to 15,550.
In this paper, I focus on the region from 21,563 to 29,674 because this is a much longer contiguous sequence and because the amplicons were generated by a single rather than nested PCR, which reduces the risk of PCR artifacts.

>>>>

\subsection{The data are sufficient to determine the viral sequence from the start of spike through the end of ORF10 for many samples}
The approach described by \citet{wang2020medRxiv} involved sequencing PCR amplicons covering nucleotide sites {\color{red} FIX REGION} 21,563 to 29,674 of the SARS-CoV-2 genome, which spans from the start of the spike gene to the end of ORF10.
The approach also involved sequencing a short amplicon generated by nested PCR that covered a fragment of ORF1ab spanning sites $\sim$15,080 to 15,550.
In this paper, I focus on the region from 21,563 to 29,674 because this is a much longer contiguous sequence and because the amplicons were generated by a single rather than nested PCR, which reduces the risk of PCR artifacts.
